Energy and the CES production function

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
A few more ### comments

<<Fitted_and_Residuals>>=
temp_data_exp <- 
  leaf_apply(
    modelsExp, class=c("lm"), 
    f = function(model, id){
      ### Why wrap in data.frame() something that already is a tbl_df?  If this is necessary, say why.
      #  df <- data.frame(select(model$data, Year, Country))
      ### Also: let's use a consistent style for the dplyr commands, prefering to use %>% in most cases.
      ### Also: The following use of white space makes it clearer what is going on (and how many steps 
      ###       are involved.  I'm going to change A LOT of code to this format.
      ### In this format, there is no name to create a temporary variable (or to use return())

@@

<<Fitted_and_Residual_Graph_Functions>>=
fittedGraphNoCSP <- function(data){
  fittedGraphData <- 
    data %>% 
    select(Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest) %>%
    melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
         value.name = "value", variable.name = "variable") %>%
    mutate(label = paste(variable, energy)) %>%
  # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
    filter(label %in% c("iGDP With energy", "fittedExp With energy", 
                        "fitted With energy", "fitted Without energy")
    ) %>% 
    mutate(
      label = plyr::mapvalues(label, 
        from = c("iGDP With energy",  "fittedExp With energy",
                 "fitted With energy", "fitted Without energy"), 
        to = c("GDP",  "Reference model",
               "With energy", "Without energy")),
      label = relevelFactor(factor(label), 
                            c("GDP", "Reference model", "Without energy", "With energy"))
    )

>>>>

<<Fitted_and_Residuals>>=
### Why are we going back and forth between CamelCase and interspersed_underscores?
### If there isn't a reason, probably we should stick with one naming convention.

temp_data_exp <- 
  leaf_apply(
    modelsExp, class=c("lm"), 
    f = function(model, id){
      ### Why wrap in data.frame() something that already is a tbl_df?  If this is necessary, say why.
      #  df <- data.frame(select(model$data, Year, Country))
      ### Also: let's use a consistent style for the dplyr commands, prefering to use %>% in most cases.
      ### Also: The following use of white space makes it clearer what is going on (and how many steps 
      ###       are involved.  I'm going to change A LOT of code to this format.
      ### In this format, there is no name to create a temporary variable (or to use return())

@@

<<Fitted_and_Residual_Graph_Functions>>=

### Can fittedGraphNoCSP and fittedGraphCSP be combined into one function with an argument?
### Or can the data filtering happen outside and everything else be the same?
### Did you copy and paste to make one from the other?  That should be a sign...
fittedGraphNoCSP <- function(data){
  fittedGraphData <- 
    data %>% 
    select(Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest) %>%
    melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
         value.name = "value", variable.name = "variable") %>%
    mutate(label = paste(variable, energy)) %>%
  # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
    filter(label %in% c("iGDP With energy", "fittedExp With energy", 
                        "fitted With energy", "fitted Without energy")
    ) %>% 
    mutate(
      label = plyr::mapvalues(label, 
        from = c("iGDP With energy",  "fittedExp With energy",
                 "fitted With energy", "fitted Without energy"), 
        to = c("GDP",  "Reference model",
               "With energy", "Without energy")),
      label = relevelFactor(factor(label), 
                            c("GDP", "Reference model", "Without energy", "With energy"))
    )
